Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra

### 2024-05-21 paper/main.tex
update photos in draft
add in weighted avg, fix figure label

\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{amsmath, amsfonts, amssymb, mathrsfs}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filemod}
\usepackage{natbib}
\usepackage[ruled, vlined]{algorithm2e}
\usepackage{floatrow}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=4in]{plot_data.png}
    \caption{The perturbation theory, low resolution runs, and high resolution run for the first training cosmology. The weighted average is also shown as a dashed line. Dotted lines at the bottom indicate where each data type is deemed approximately unbiased.}
    \label{fig:plot_data}
\end{figure}

From the multiple low- and high-resolution spectra across all cosmologies, \cite{moran2023mira} obtain estimates for the precision of these spectra across the $n$ wavenumber values ($p_1,\dots,p_n$) using a log-log regression model, and a multiplier $c$ for the increase in precision from the low- to high- resolution output. Given that the perturbation theory spectra is non-stochastic, we treat this as having a precision of $10^6$. We leverage these precision estimates within our model and calculate a weighted average for each cosmology: $\bar y = AddThisIn$, \textcolor{blue}{where we have four diagonal covariance matrices.}

@@

>>>>

\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{amsmath, amsfonts, amssymb, mathrsfs, dsfont}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filemod}
\usepackage{natbib}
\usepackage[ruled, vlined]{algorithm2e}
\usepackage{floatrow}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_data.png}
    \caption{The perturbation theory, low resolution runs, and high resolution run for the first training cosmology. The weighted average is also shown as a dashed line. Dotted lines at the bottom indicate where each data type is deemed approximately unbiased.}
    \label{fig:plot_data}
\end{figure}

From the multiple low- and high-resolution spectra across all cosmologies, \cite{moran2023mira} obtained estimates for the precision of these spectra across the $n$ wavenumber values ($p_1,\dots,p_n$) using a log-log regression model, and a multiplier $c$ for the increase in precision from the low- to high- resolution output. Given that the perturbation theory spectra is non-stochastic, we treat this as having a precision of $10^5$. We leverage these precision estimates within our model at each data type's unbiased wavenumber values to define $\Lambda_p = \text{diag}\left((10^5)_{k < 0.04}\right)$, $\Lambda_{\ell} = \text{diag}\left((p_1,\dots,p_n)_{0.04 \leq k < 0.25}\right)$, $\Lambda_h = \text{diag}\left(c(p_1,\dots,p_n)_{0.04 \leq k \leq 5}\right)$. Here, each precision matrix is diagonal and the diagonal elements consists of the precision values or zero, depending on whether the $k$ value is approximately unbiased for that data type. With this, we calculate a weighted average for each cosmology: $\bar y = \Lambda_S^{-1}(\Lambda_p y_p + \Lambda_h y_h + \Lambda_{\ell} \bar{y}_\ell)$, where $\Lambda_S = \Lambda_p + \Lambda_\ell + \Lambda_h$ is the precision matrix for the weighted average for a particular cosmology.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_fit.png}
    \caption{95\% credible intervals for the power spectrum of model 1 (posterior mean subtracted). Plots of the perturbation theory, low-resolution and high-resolution runs are also shown, alongside the weighted average.}
    \label{fig:plot_fit}
\end{figure}
